Report

### 2022-07-19 manuscript.Rmd
Rewrite opening paragraph of tutorial

# Tutorial
This tutorial about Bayesian Evidence Synthesis (BES) requires installation of `r R.Version()$version.string`, Rstudio version `r RStudio.Version()$version` and package `bain` version `r packageVersion('bain')`. 
This tutorial focusses on synthesizing evidence for an informative hypotheses using the Product Bayes Factor (pbf). 
To illustrate the method, a simulated counterpart of the data used in [@vanleeuwen2022morality] will be used available in `bain`. 
The data is used to investigate the relationship between political orientation and moral dispositions in three countries: the United states of America, Denmark and the Netherlands. 
A more detailed description of the dataset is either provided in [@vanleeuwen2022morality] or by running `?bain::synthetic_us`, `?bain::synthetic_dk` or `?bain::synthetic_nl`.

>>>>

# Tutorial

This tutorial about Bayesian Evidence Synthesis (BES) requires R-package `bain` version `r packageVersion('bain')` or later.
This tutorial focusses on synthesizing evidence for an informative hypotheses using the Product Bayes Factor (pbf). 
The data used to illustrate the method have been simulated based on the data presented in [@vanleeuwen2022morality].
These simulated data are available in the `bain` package. 
A more detailed description of the dataset is either provided in [@vanleeuwen2022morality] or by running `?bain::synthetic_us`, `?bain::synthetic_dk` or `?bain::synthetic_nl`.
The research question is whether there is an association between political orientation and moral dispositions.
Suitable data were collected in three countries: the United states of America, Denmark and the Netherlands.
Each sample contains multiple measures of political orientation and moral dispositions.
In the original publication, the PBF was used to aggregate evidence across scales and countries to obtain an overall measure of support for the central hypothesis.
This tutorial follows the same rationale, but uses only one effect size per sample,
and varies the way this effect size is computed to illustrate different use cases.
